\documentclass[a4paper, oneside, 10pt, final]{amsart}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[babel=true,kerning=true]{microtype}

\usepackage{amsmath, amssymb}
\usepackage{eucal}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{amsaddr}
\usepackage{standalone}
\usepackage{caption}

\usepackage{stmaryrd}
\usepackage[noend]{algpseudocode}

\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{backgrounds}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}

\def\osrank{\textsc{\small{osrank}}}
\def\oscoin{\textsc{\small{oscoin}}}
\def\netgraph{\mathcal{N}}
\def\accounts{\mathcal{A}}
\def\state{\mathcal{S}}
\def\ledger{\mathcal{L}}
\def\users{\mathcal{U}}
\def\projs{\mathcal{P}}
\def\miners{\mathcal{M}}
\def\registry{\mathcal{R}}
\def\bal{\mathsf{bal}}
\def\depend{\mathsf{depend}}
\def\undepend{\mathsf{undepend}}
\def\seedset{\Upsilon}
\def\epoch{\kappa}
\def\pagerank{PageRank}
\def\protocol{\Phi}

\newcommand{\tuple}[1]{\langle#1\rangle}
\newcommand{\mathsc}[1]{\text{\normalfont\scshape#1}}
\newcommand{\dep}{\xrightharpoondown[e]{d}}
\newcommand{\tx}[2]{\mathsf{#1}\lparen#2\rparen}
\newcommand{\field}[2]{#1_{\mathsf{#2}}}
\newcommand{\fn}[2]{\operatorname{#1}(#2)}
\newcommand{\prop}[2]{#1.{\mathrm{#2}}}

\newcommand*\eg{e.g.\ }
\newcommand*\ie{i.e.\ }

\algrenewcommand\algorithmicprocedure{\textbf{handler}}

% No paragraph indentation after section headers.
\makeatletter
\let\@afterindenttrue\@afterindentfalse
\makeatother

\newenvironment{fig}
  {\par\noindent\minipage{\linewidth}}
  {\endminipage\bigskip}

\newenvironment{epigraph}[2][]
{\leftskip=1cm \def\epigraph@author{#2} \smallskip\itshape}
{\par\vspace{0.5em}\normalfont\hfill---\ \Small\epigraph@author\hspace*{0.2cm}\par\medskip}
\makeatother

\setlist[description]{leftmargin=0.8cm, labelindent=\parindent}
\setlist[itemize]{leftmargin=0.8cm, labelindent=\parindent}
\setlist[enumerate]{leftmargin=0.8cm, labelindent=\parindent}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-4cm}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-4cm}

\raggedcolumns
\calclayout

\makeatletter
\let\@wraptoccontribs\wraptoccontribs
\makeatother

\begin{document}

\title[open source coin]{open source coin \\ \vspace{0.5em}\Small{trust and sustainability in open source communities} \\ {\tiny Draft 1.0}}
\author{\Small Alexis Sellier\textsuperscript{$\dagger$} \qquad Eleftherios Diakomichalis\textsuperscript{$\dagger$} \qquad James Haydon\textsuperscript{$\dagger$}}
\date{February 2019}

\thanks{\textsuperscript{$\dagger$}Monadic, \texttt{\{alexis,ele,james\}@monadic.xyz}}

\begin{abstract}
The success of the open source movement stems from its dynamic culture of
peer-to-peer distribution and collaboration. Yet, as open source has grown from
free \emph{software ideal} to \emph{industry standard}, sustainable financing
has become a pressing problem.  Here we propose open source coin or
\textsc{oscoin}, a secure peer-to-peer protocol for developing a sustainable
open source economy, as well as a platform for establishing trust and
transparency in open source communities.
\end{abstract}

\maketitle

\setlength{\columnsep}{1cm}
\begin{multicols}{2}

\input{sections/01-background.tex}
\input{sections/02-oscoin.tex}
\input{sections/03-osrank.tex}
\input{sections/04-ledger.tex}
\input{sections/05-smart-contracts.tex}
\pagebreak
\input{sections/06-applications.tex}

\section*{Acknowledgements}
We thank Sam Hart for his clear thinking, feedback and contributions to some of
the core ideas presented in this work. We thank Aaron Levin for his contributions
and great discussions early on in the process of conceiving \oscoin{}.

% TODO: fix formatting in refs, or use bibtex or something.
\begin{thebibliography}{9}

\bibitem{bitcoin} Nakamoto, Satoshi. Bitcoin: A Peer-to-Peer Electronic Cash
  System. May 2009

\bibitem{ethereum} Wood, Gavin. Ethereum: A Secure Decentralised Generalised
  Transaction Ledger. December 2018

\bibitem{roads and bridges} Eghbal, Nadia. Roads and Bridges. The Unseen labor
  behind our digital infrastructure. July 2016.

\bibitem{pagerank} Brin, S.; Page, L. (1998). The anatomy of a
  large-scale hypertextual Web search engine (PDF). \emph{Computer Networks
  and ISDN Systems.} 30: 107–117.

\bibitem{pagerank-sybil} Cheng, A. and Friedman, E. 2006. Manipulability of
  PageRank under Sybil strategies. In First Workshop on the Economics of
  Networked Systems (NetEcon06).

\bibitem{trustrank} Z. Gyöngyi, H. Garcia-Molina, J. Pedersen: Combating Web
  Spam with TrustRank

\bibitem{incr pagerank} Bahmani, Bahman and Chowdhury, Abdur and Goel,
  Ashish. Fast Incremental and Personalized PageRank. Proc. VLDB
  Endow. December 2010.

\bibitem{nix} Dolstra, E., de Jonge, M. and Visser, E. Nix: A Safe and
  Policy-Free System for Software Deployment. In Damon, L. (Ed.), 18th Large
  Installation System Administration Conference (LISA '04), pages 79–92, Atlanta,
  Georgia, USA. USENIX, November 2004.

\end{thebibliography}

\end{multicols}
\end{document}
